Paper \#ZW10157

### 2018-12-21 paper/submission/ZW10157-response-1.tex
more responses added

{\bf My response:} {\color{blue} The grid has been removed from Figures 10 and 11.
PDF versions of the tikz pictures have been made. All updated figures are provided 
along with an updated source file.}

{\bf Referee A (Remarks to Author)}

@@

{\bf My response:} {\color{blue} The code sections have been removed.}

@@

{\bf My response:} {\color{blue} XXXXX.}

REFEREE B - ZW10157

@@

{\bf My response:} {\color{blue} XXXXX.}

@@

line 35: trade of -> trade off

{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}

@@

subsubsection 3

line 427 to to -> to

{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}

subsubsection 4

FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
FIG. 11. Explain why a nonfront solution is used otherwise the
optimization exercise is moot.

@@

>>>>

{\bf Our response:} {\color{blue} The grid has been removed from Figures 10 and 11.
PDF versions of the tikz pictures have been made. All updated figures are provided 
along with an updated source file.}

{\bf REFEREE A (Remarks to Author)}

@@

{\bf Our response:} {\color{blue} The code sections have been removed.}

@@

{\bf Our response:} {\color{blue} XXXXX.}

{\bf REFEREE B (Remarks to Author)}

@@

{\bf Our response:} {\color{blue} XXXXX.}

@@

line 35: trade of -$>$ trade off

{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}

@@

{\bf Our response:} {\color{blue} The code has been removed from the updated manuscript. Interested parties can refer to the repository.}

subsubsection 3:
line 427 to to -$>$ to

{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}

subsubsection 4:
FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
FIG. 11. Explain why a nonfront solution is used otherwise the
optimization exercise is moot.

{\bf Our response:} {\color{blue} This was a plotting mistake, and has been corrected in the updated Fig. 11.}

@@

{\bf Our response:} {\color{blue} This table shows input parameters for one optimized solution (the solution in Fig. 12). 
The table title has been changed to the following: "Input Parameters for the optimized solution shown in Figures~11 and 12."}
